The Young Planet DS Tuc Ab has a Low Obliquity

### 2019-10-18 paper/main.tex
more words

\correspondingauthor{Benjamin~T.~Montet; \twitter{benmontet}}
\email{b.montet@unsw.edu.au}

@@

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.5\textwidth, trim={0cm 0.0cm 1cm 1cm}, clip=true]{../figures/model_comp.pdf}
   \end{center}
  \caption{Draws from the posterior distributions of a simultaneous fit to the
  Rossiter-McLaughlin signal and three different noise models. Green curves represent the noise model, while orange curves include the transit signal as well. From top to bottom, the noise models are a simple cubic polynomial fit, a fit regressed against the spectral stellar activity indicators, and a starspot model built with the \textit{starry} package of \citep{Luger19}. The polynomial and starspot models provide similar quality fits to the data, both of which find significantly higher log likelihood values than the third fit. Significantly, all give consistent results on the measured spin-orbit obliquity angle of approximately $12 \pm 12$ degrees.}
  \label{fig:models}
\end{figure}

@@

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.5\textwidth, trim={0cm 0.0cm 0cm 0cm}, clip=true]{../figures/lcs.pdf}
   \end{center}
  \caption{(Left) DS Tuc A light curve from the \tess\ Sector 1 Full-Frame Images, built with the \eleanor\ pipeline of \citet{Feinstein19}. (Right) ASAS-SN light curve for the same star, with the \tess\ light curve overlaid in red. While \tess\ shows a 4\% variability on rotational timescales, the star itself varies on multi-year timescales by as much as 30\%, suggesting significant starspot coverage on the stellar surface. The brightest cadences observed with \tess\ are approximately 10\% fainter than the brightest observations with ASAS-SN.}
  \label{fig:lc_data}
\end{figure}

@@

We thank \btmtodo{people including Michael Gully-Santiago and Leslie Rogers} for \btmtodo{things}.

>>>>

%\correspondingauthor{Benjamin~T.~Montet; \twitter{benmontet}}
\email{b.montet@unsw.edu.au}

@@

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.45\textwidth, trim={0cm 0.0cm 1cm 1cm}, clip=true]{../figures/model_comp1.pdf}
   \end{center}
  \caption{Draws from the posterior distributions of a simultaneous fit to the
  Rossiter-McLaughlin signal and three different noise models. Green curves represent the noise model, while orange curves include the transit signal as well. From top to bottom, the noise models are a simple cubic polynomial fit, a fit regressed against the spectral stellar activity indicators, and a starspot model built with the \textit{starry} package of \citep{Luger19}. The polynomial and starspot models provide similar quality fits to the data, both of which find significantly higher log likelihood values than the third fit. Significantly, all give consistent results on the measured spin-orbit obliquity angle of approximately $12 \pm 12$ degrees.}
  \label{fig:models}
\end{figure}

@@

\begin{figure}[!tbh]
  \begin{center}
    \includegraphics[width=0.5\textwidth, trim={0cm 0.0cm 0cm 0cm}, clip=true]{../figures/lcs1.pdf}
   \end{center}
  \caption{(Left) DS Tuc A light curve from the \tess\ Sector 1 Full-Frame Images, built with the \eleanor\ pipeline of \citet{Feinstein19}. (Right) ASAS-SN light curve for the same star, with the \tess\ light curve overlaid in green. While \tess\ shows a 4\% variability on rotational timescales, the star itself varies on multi-year timescales by as much as 30\%, suggesting significant starspot coverage on the stellar surface. The brightest cadences observed with \tess\ are approximately 10\% fainter than the brightest observations with ASAS-SN.}
  \label{fig:lc_data}
\end{figure}

@@

We thank \btmtodo{people including George Zhou and Leslie Rogers} for \btmtodo{things}.
